%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
% Salesforce
%---------------------------------------------------------
\cventry
{Principal Backend Software Engineer} % Job title
{Salesforce} % Organization
{Bellevue WA, USA} % Location
{Aug. 2021 } % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item
    {
      Designed and implemented a new feature in Automation Studio (Marketing Cloud application).
    }
    \item
    {
      Investigated production performance and avability issues (various Marketing Cloud services).
    }
    \item
    {
      Mentored team members in managed code debugging.
    }
    \item
    {
      Technologies:\\
      {C\#}, WinDbg.
    }
  \end{cvitems}
}

%---------------------------------------------------------
% Microsoft Redmond
%---------------------------------------------------------

%---------------------------------------------------------
\cventry
{Principal Software Engineer} % Job title
{Microsoft Corporation - SQL Server} % Organization
{Redmond WA, USA} % Location
{Oct. 2013 - Aug. 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item 
    { 
      Worked on various aspects of the SQL Server engine, in the servicing and the core teams.
      Improved and implemented bug fixes in many areas of SQL Server engine, support tools and client drivers.
    }
    \item
    {
      Worked on the integration of MLOS with SQLServer to enable database engine performance optimization:\\
      \scriptsize
      \url{http://github.com/microsoft/mlos}
    }
    \item
    {
      Co-authored a DEEM 2020 paper:\\
      \scriptsize
      \url{https://arxiv.org/pdf/2006.02155.pdf}
    }
    \item
    { 
      Implemented new, {C\#} based debugging tools for SQLServer engine leveraging code generation based on the pdb files.
    }
    \item
    {
      SqlCLR Host maintainer. \\
      \scriptsize
      \url{https://docs.microsoft.com/en-us/dotnet/framework/data/adonet/sql/introduction-to-sql-server-clr-integration}
    }
    \item
    {
      Implemented SQLServer big data cluster data pools. \\
      \scriptsize
      \url{https://docs.microsoft.com/en-us/sql/big-data-cluster/concept-data-pool}
    }
    \item
    {
      Enabled debugging of .NET applications (via MSVSMON) for user-mode implementation of NT kernel. \\
      \scriptsize
      \url{https://cloudblogs.microsoft.com/sqlserver/2016/12/16/sql-server-on-linux-how-introduction}
    }
    \item
    {
      Technical lead on the Extensibility team. Ported SQL Satelite to Linux OS. \\
      \scriptsize
      \url{https://docs.microsoft.com/en-us/sql/advanced-analytics/concepts/extensibility-framework}
    }
    \item
    {
      Implemented native spatial feature and other performance improvements: \\
      \scriptsize
      \url{https://blogs.msdn.microsoft.com/bobsql/2016/06/03/sql-2016-it-just-runs-faster-spatial-index-builds-faster} \\
      \url{https://blogs.msdn.microsoft.com/bobsql/2016/06/03/sql-2016-it-just-runs-faster-tvps-with-spatial-columns} \\
      \url{https://blogs.msdn.microsoft.com/bobsql/2016/06/03/sql-2016-it-just-runs-faster-tvps-with-spatial-columns} \\
      \url{https://blogs.msdn.microsoft.com/psssql/2016/03/03/sql-2016-it-just-runs-faster-native-spatial-implementations}
      }
    \item
    {
      Improved peformance of managed XEvent Linq readers: \\
      \scriptsize
      \url {https://blogs.msdn.microsoft.com/psssql/2016/05/18/sql-2016-it-just-runs-faster-xevent-linq-reader/}
    }
    \item
    { 
      Part of SSMS QDS UI team: \\
      \scriptsize
      \url {https://docs.microsoft.com/en-us/sql/relational-databases/performance/monitoring-performance-by-using-the-query-store}
    }
    \item
    {
      Implemented SSMS compare plans feature and new plan layout algorithm: \\
      \scriptsize
      \url {https://www.sqlshack.com/how-to-compare-query-execution-plans-in-sql-server-2016} \\
      \url {https://www.dotnine.net/ssms-preview-plan-comparison-tool-and-plan-viewer-optimizations}
    }
    \item
    {
      Build System Engineering.
    }
    \item
    {
      Technologies: \\
      C++, {C\#}, NetFX, NetCore, gRPC, WinDbg, WPF.
    }
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer in Test} % Job title
{Microsoft Corporation - Azure Networking} % Organization
{Redmond WA, USA} % Location
{May. 2012 - Oct. 2013} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item
    {
      Designed and implemented deployment service for PaaS and IaaS tenants. 
      Created new test framework - Remote Cluster Repository.
    }
    \item
    {
      Designed and implemented code coverage collection for SLB (Software Load Balancer).
    }
    \item
    {
      Owned SLB functional tests for the following features:
      Cross Cluster support and Route Aggregation.
    }
    \item
    {
      Technologies: \\
      {C\#}, Azure, Magellan (code coverage tool), Detour, WCF, Remote LinQ.
    }
  \end{cvitems}
}

%---------------------------------------------------------
% Microsoft Dublin
%---------------------------------------------------------

%---------------------------------------------------------
\cventry
{Software Engineer in Test} % Job title
{Microsoft Corporation - Azure Networking} % Organization
{Dublin, Ireland} % Location
{May. 2009 - May. 2012} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item
    {
      Designed and implemented test architecture for Azure DNS service.
      Responsible for all aspects of service testing. \\
      Developed innovative test framework RCES – remote code execution and code injection framework – 
      to simplify distributed testing and enable fault testing in a heterogeneous environment.
    }
    \item
    {
      Technologies: \\
      {C\#}, IL, Azure, WCF, WinDbg (Windows Debugging Tools).
    }
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Microsoft Corporation - Windows Phone 7} % Organization
{Dublin, Ireland} % Location
{May. 2008 - May. 2009} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item
    {
      Worked on the software application designed to monitor network usage and help users manage their data plans, including driver-level components, web services, and UI.
      Responsible for the architecture, design, and implementation of the system to capture and filter network data traffic and for the cost estimation engine.
    }
    \item
    {
      Technologies:\\
      C++, Windows Mobile 6, Windows Mobile 7, Visual Studio 2008, Platform Builder, NDIS Lightweight Filter (LWF) driver, MS SQL Server 2008.
    }
  \end{cvitems}
}

%---------------------------------------------------------
% EMCC
%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{EMCC Software Ltd} % Organization
{Manchester, UK} % Location
{June. 2007 - May. 2008} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item
    {
      Worked on BlackBerry push email client for Sony Ericsson mobile phones.
    }
    \item
    {
      Technologies:\\
      C++, Code Warrior, Symbian SDK v 9, UIQ 3.s
    }
  \end{cvitems}
}

%---------------------------------------------------------
% Ideal Host
%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Ideal Host Poland} % Organization
{Gdansk, Poland} % Location
{Jul. 2005 - May. 2007} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item
    {
      Acted as application architect and lead developer for the line of business system
      designed and developed for the multimillion-pound UK Joint Industry Board for Plumbers.
      Responsible for all aspects of the organization, including the UK government CSCS scheme and NVQ distribution.
    }
    \item
    {
      Technologies:\\
      {C\#}, .NET 2.0, Windows Forms, MS SQL Server 2005, MS SQL Server 2005 Reporting Services, Crystal Reports.
    }
  \end{cvitems}
}

%---------------------------------------------------------
% Axiom Software
%---------------------------------------------------------
\cventry
{Co-Founder} % Job title
{Axiom Software} % Organization
{Gdansk, Poland} % Location
{Jan. 2004 - Jul. 2005} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item
    {
      Designed and developed a system to improve the management of sales representatives' work. The system allows instant invoice and order creation, design and completion of marketing questionnaires, schedule management, task management, accounting for distances traveled, and sales report generation.
      Successfully deployed product to several food distribution companies with full integration with existing company management system. \\
      Responsible for complete product cycle, including sales and marketing.
    }
    \item
    {
      Developed an application on Pocket PC platform to track and record GPS position. This application loaded maps with ArcView format and displayed details of the current user position.
    }
    \item
    {
      Technologies:\\
      Microsoft Visual C++ 6.0, MS Embedded Visual C++, .NET Framework 1.1,
      .NET Remoting, gSoap (C++ web services framework), MS Embedded Visual C++,
      MS SQL Server 2000, SQL Server CE 2.0, SQL Server Merge Replication.
    }
  \end{cvitems}
}

%---------------------------------------------------------
% Ivo
%---------------------------------------------------------
\cventry
{Software Developer} % Job title
{IVO Software (now Amazon Text to Speech)} % Organization
{Gdansk, Poland} % Location
{Aug. 2001 - Dec. 2003} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item
    {
      Ported the voice synthesizer (Polish language) to Symbian platform S60, implemented audio streaming.
    }
    \item
    {
      Implemented SAPI 4.0 Speech Server, an interface for speech synthesizer used as integration with screen reader application.
    }
    \item
    {
      Designed and implemented UniSpeaker, an application designed for visually impaired people.
      The application reads the clipboard, the keyboard strokes, and new messages on your email account.
    }
    \item
    {
      Improved the reliability of the Speech Synthesizer security protection.
    }
    \item
    {
      Technologies:\\
      Microsoft Visual C++ 6.0, Symbian SDK, ActiveX - ATL, COM, Win API, x86 Assembler.
    }
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
